---
title: "<h2>Data Harvesting - Final project: Visualization </h2>"
output: html_document
---

```{=html}
<style>
body {
text-align: justify}
</style>
```
\

### Visualization of the scraped Stock Market indexes

This script contains charts and visualization generated using the scraped data of the stock Market indexes obtained from [Yahoo Finance](https://es.finance.yahoo.com/) and [Investing](https://www.investing.com/). It demonstrates how the scraped data can be used to facilitate the visualization of the indexes extracted from the websites, showing the evolution of the stock market over the day.\

**Libraries**

```{r warning=FALSE, message=FALSE}


library(rmarkdown)
library(knitr)
library(scrapex)
library(rvest)
library(httr)
library(dplyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(tools)
library(taskscheduleR)
library(stringr)
library(readr)
library(ggpubr)
library(ggrepel)

```

\

### 1. World Index

#### Read scraped data stored in the generated CSV files:

```{r warning=FALSE, message=FALSE}


csv_world <- list.files(pattern = "^world.*\\.csv$", full.names = TRUE)

list_world <- lapply(csv_world, read_csv) 

data_world<- do.call(rbind, list_world)
data_world <- data_world %>% 
  mutate(Date = substr(Date, 1, 5))

```

\

#### **European Index Evolution:**

```{r, echo=TRUE,warning=FALSE, message=FALSE, fig.align='center', fig.width=10, fig.height=6, collapse=TRUE}

colors <- c("IBEX" = "seagreen2", "GDAXI" = "coral", "FCHI" = "mediumblue", "ATX" = "magenta1", "FTSE" = "yellow1", "BFX" = "deeppink")
european_stock <- data_world |> 
  filter(Simbolo %in% c("IBEX", "GDAXI", "FCHI","ATX", "FTSE", "BFX")) 



limits_df <- european_stock %>%
  group_by(Simbolo) %>%
  summarize(ymin = min(Ultimo_precio),
            ymax = max(Ultimo_precio))

european_stock <- merge(european_stock, limits_df, by = "Simbolo")

plot <- ggplot(european_stock, aes(x = Date, y = Ultimo_precio, color = Simbolo, group = Simbolo)) +
  geom_point(size = 2) +   
  geom_line(size = 1, aes(color = Simbolo))  + 
  facet_wrap(~ Simbolo, scales = "free_y") +
  geom_text_repel(aes(label = round(Ultimo_precio, 2)), size = 3, vjust = -2.2, segment.size = 0, segment.color = NA) +
  labs(x = NULL, y = "Last Price", title = "European Index Evolution") +
  theme(
    panel.background = element_rect(fill = "black"),
    plot.background = element_rect(fill = "black"),
    plot.title = element_text(color = "white", margin = margin(b = 30)),  # Move the title upwards
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    axis.text.x = element_text(color = "white", angle = 45, hjust = 1, size = 6),  
    axis.text.y = element_text(color = "white",  hjust = 1),
    axis.title.y = element_text(color = "white", size = 8, margin = margin(r = 12)),  # Move the y-axis title to the left
    strip.background = element_blank(),  
    strip.text.x = element_text(size = 9, color = "white", face = "bold"),
    plot.margin = margin(10, 18, 10, 15)) +  #top, right, bottom, left
  geom_blank(aes(y = ymin, ymax = ymax)) + 
  guides(color = FALSE, fill = FALSE) +
  scale_color_manual(values = colors) 


print(plot)


```

\

#### Iterative European stock market evolution

```{r, echo=TRUE,warning=FALSE, message=FALSE, fig.align='center', fig.width=10, fig.height=6, collapse=TRUE}

library(plotly)

ggplotly(plot, tooltip=c("Ultimo_precio"))

```

\

-   **IBEX-35 Index plot**

```{r, echo=TRUE,warning=FALSE, message=FALSE, fig.align='center', fig.width=10, fig.height=6, collapse=TRUE}


g_es <-
data_world %>%
  filter(Simbolo == "IBEX") %>% 
  ggplot(aes(x = Date, y = Ultimo_precio, color = Simbolo, group = Simbolo)) +
  geom_point(size = 2) +   # Add points
  geom_line(size = 1,color = "seagreen2") +
  labs( x=NULL,y="Last Price", title="IBEX 35 INDEX EVOLUTION") +
  theme(panel.background = element_rect(fill = "black"),
        plot.background = element_rect(fill = "black"),
        plot.title = element_text(color = "white"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
       panel.grid.major.x = element_blank(),
       panel.grid.minor.x = element_blank(),
       axis.text = element_text(color = "white"),   
      axis.title = element_text(color = "white")) +
  scale_color_manual(values = c("IBEX" = "seagreen2")) +
  guides(color=FALSE, fill=FALSE) 
  

ggplotly(g_es, tooltip=c("Ultimo_precio"))


```

\

-   **DAX Index plot**

```{r, echo=TRUE,warning=FALSE, message=FALSE, fig.align='center', fig.width=10, fig.height=6, collapse=TRUE}


g_al<-
data_world |> 
  filter(Simbolo == "GDAXI") |> 
  ggplot(aes(x = Date, y = Ultimo_precio, color = Simbolo, group = Simbolo)) +
  geom_point(size = 2) +   
  geom_line(size = 1,color = "coral") +
  labs(x=NULL,y="Last Price", title="DAX INDEX EVOLUTION") +
  theme(panel.background = element_rect(fill = "black"),
        plot.background = element_rect(fill = "black"),
        plot.title = element_text(color = "white"),
        panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    axis.text = element_text(color = "white"),   
        axis.title = element_text(color = "white")) +
  scale_color_manual(values = c("GDAXI" = "coral")) +
  guides(color=FALSE, fill=FALSE)


ggplotly(g_al, tooltip=c("Ultimo_precio"))
```

\

-   **CAC40 Index plot**

```{r, echo=TRUE,warning=FALSE, message=FALSE, fig.align='center', fig.width=10, fig.height=6, collapse=TRUE}

g_fr <-data_world |> 
  filter(Simbolo == "FCHI") |> 
  ggplot(aes(x = Date, y = Ultimo_precio, color = Simbolo, group = Simbolo)) +
  geom_point(size = 2) +   
  geom_line(size = 1,color = "mediumblue")  +
  labs(x=NULL,y="Last Price", title="CAC 40 INDEX EVOLUTION") +
  theme(panel.background = element_rect(fill = "black"),
        plot.background = element_rect(fill = "black"),
        plot.title = element_text(color = "white"),
        panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    axis.text = element_text(color = "white"),   
        axis.title = element_text(color = "white")) +
  scale_color_manual(values = c("FCHI" = "mediumblue")) +
  guides(color=FALSE, fill=FALSE)

ggplotly(g_fr, tooltip=c("Ultimo_precio"))

```

\

-   **FTSE 100 Index plot**

```{r, echo=TRUE,warning=FALSE, message=FALSE, fig.align='center', fig.width=10, fig.height=6, collapse=TRUE}

g_uk<-data_world |> 
  filter(Simbolo == "FTSE") |> 
  ggplot(aes(x = Date, y = Ultimo_precio, color = Simbolo, group = Simbolo)) +
  geom_point(size = 2) +   
  geom_line(size = 1,color = "magenta1") +
  labs(x=NULL,y="Last Price", title="FTSE 100 INDEX EVOLUTION") +
  theme(panel.background = element_rect(fill = "black"),
        plot.background = element_rect(fill = "black"),
        plot.title = element_text(color = "white"),
        panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    axis.text = element_text(color = "white"),   
        axis.title = element_text(color = "white")) +
  scale_color_manual(values = c("FTSE" = "magenta1")) +
  guides(color=FALSE, fill=FALSE)

ggplotly(g_uk, tooltip=c("Ultimo_precio"))
```

\

-   **ATX Index plot**

```{r, echo=TRUE,warning=FALSE, message=FALSE, fig.align='center', fig.width=10, fig.height=6, collapse=TRUE}


g_aus <- data_world |> 
  filter(Simbolo == "ATX") |> 
  ggplot(aes(x = Date, y = Ultimo_precio, color = Simbolo, group = Simbolo)) +
  geom_point(size = 2, color = "yellow1") +   
  geom_line(size = 1,color = "yellow1")  + 
  labs(x=NULL,y="Last Price", title="ATX INDEX EVOLUTION") +
  theme(panel.background = element_rect(fill = "black"),
        plot.background = element_rect(fill = "black"),
        plot.title = element_text(color = "white"),
        panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    axis.text = element_text(color = "white"),   
        axis.title = element_text(color = "white")) +
  scale_color_manual(values = c("FTSE" = "yellow1")) +
  guides(color=FALSE, fill=FALSE)


ggplotly(g_aus, tooltip=c("Ultimo_precio"))

```

\

-   **BEL20 Index plot**

```{r, echo=TRUE,warning=FALSE, message=FALSE, fig.align='center', fig.width=10, fig.height=6, collapse=TRUE}


g_bel <- data_world |> 
  filter(Simbolo == "BFX") |> 
  ggplot(aes(x = Date, y = Ultimo_precio, color = Simbolo, group = Simbolo)) +
  geom_point(size = 2) +   
  geom_line(size = 1,color = "deeppink")+
  labs(x=NULL,y="Last Price", title="BFX INDEX EVOLUTION") +
  theme(panel.background = element_rect(fill = "black"),
        plot.background = element_rect(fill = "black"),
        plot.title = element_text(color = "white"),
        panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    axis.text = element_text(color = "white"),   
        axis.title = element_text(color = "white")) +
  scale_color_manual(values = c("BFX" = "deeppink")) +
  guides(color=FALSE, fill=FALSE)

ggplotly(g_bel, tooltip=c("Ultimo_precio"))
```

\

### 2. IBEX-35

-   Read scraped data stored in the generated CSV files:

```{r warning=FALSE, message=FALSE, echo=TRUE, collapse=TRUE}


csv_ibex <- list.files(pattern = "^ibex.*\\.csv$", full.names = TRUE)

list_ibex <- lapply(csv_ibex, read_csv)

data_ibex<- do.call(rbind, list_ibex)

data_ibex <- data_ibex %>% 
  mutate(ultimo = replace(data_ibex$ultimo, TRUE, gsub(",", ".", data_ibex$ultimo)), 
         ultimo = as.numeric(ultimo))
```

\

-   **Top IBEX-35 companies**

```{r warning=FALSE, message=FALSE, echo=TRUE, collapse=TRUE}

top_companies_ibex <- data_ibex %>%
  group_by(Nombre) %>%
  summarise(average_price = mean(ultimo, na.rm = TRUE)) %>%
  arrange(desc(average_price)) %>%
  head(5) 

colnames(top_companies_ibex) <- c("Company", "Last Price")
knitr::kable(top_companies_ibex, caption = "Top 5 Companies in Belgium", align = "c")
```

\

### 3. DAX

-   Read scraped data stored in the generated CSV files:

```{r warning=FALSE, message=FALSE, echo=TRUE, collapse=TRUE}


csv_dax <- list.files(pattern = "^dax.*\\.csv$", full.names = TRUE)
list_dax<- lapply(csv_dax, read_csv)
data_dax<- do.call(rbind, list_dax)


top_companies_dax <- data_dax %>%
  group_by(Nombre) %>%
  summarise(average_price = mean(ultimo, na.rm = TRUE)) %>%
  arrange(desc(average_price)) %>%
  head(5)  

colnames(top_companies_dax) <- c("Company", "Last Price")
knitr::kable(top_companies_dax, caption = "Top 5 Companies in Germany", align = "c")

```

\

### 4. CAC

-   Read scraped data stored in the generated CSV files:

```{r warning=FALSE, message=FALSE, echo=TRUE, collapse=TRUE}

csv_cac <- list.files(pattern = "^cac.*\\.csv$", full.names = TRUE)
list_cac<- lapply(csv_cac, read_csv)
data_cac<- do.call(rbind, list_cac)

```

\

-   **Top CAC companies**

```{r warning=FALSE, message=FALSE, echo=TRUE, collapse=TRUE}

top_companies_cac <- data_cac %>%
  group_by(Nombre) %>%
  summarise(average_price = mean(ultimo, na.rm = TRUE)) %>%
  arrange(desc(average_price)) %>%
  head(5) 

colnames(top_companies_cac) <- c("Company", "Last Price")
knitr::kable(top_companies_cac, caption = "Top 5 Companies in France", align = "c")

```

\

### 5. FTSE

-   Read scraped data stored in the generated CSV files:

```{r warning=FALSE, message=FALSE, echo=TRUE, collapse=TRUE}


csv_ftse <- list.files(pattern = "^ftse.*\\.csv$", full.names = TRUE)
list_ftse<- lapply(csv_ftse, read_csv)
data_ftse<- do.call(rbind, list_cac)

```

\

-   **Top FTSE companies**

```{r warning=FALSE, message=FALSE, echo=TRUE, collapse=TRUE}

top_companies_ftse <- data_ftse %>%
  group_by(Nombre) %>%
  summarise(average_price = mean(ultimo, na.rm = TRUE)) %>%
  arrange(desc(average_price)) %>%
  head(5)  

colnames(top_companies_ftse) <- c("Company", "Last Price")
knitr::kable(top_companies_ftse, caption = "Top 5 Companies in United Kingdom", align = "c")

```

\

### 6. ATX

-   Read scraped data stored in the generated CSV files:

```{r warning=FALSE, message=FALSE, echo=TRUE, collapse=TRUE}



csv_atx <- list.files(pattern = "^atx.*\\.csv$", full.names = TRUE)
list_atx<- lapply(csv_atx, read_csv)
data_atx<- do.call(rbind, list_atx)
```

\

-   **Top ATX companies**

```{r warning=FALSE, message=FALSE, echo=TRUE, collapse=TRUE}

top_companies_atx <- data_atx %>%
  group_by(Nombre) %>%
  summarise(average_price = mean(ultimo, na.rm = TRUE)) %>%
  arrange(desc(average_price)) %>%
  head(5)  

colnames(top_companies_atx) <- c("Company", "Last Price")
knitr::kable(top_companies_atx, caption = "Top 5 Companies in Austria", align = "c")
```

### 7. BEL

-   Read scraped data stored in the generated CSV files:

```{r warning=FALSE, message=FALSE, echo=TRUE, collapse=TRUE}



csv_bel <- list.files(pattern = "^bel.*\\.csv$", full.names = TRUE)
list_bel<- lapply(csv_bel, read_csv)
data_bel<- do.call(rbind, list_bel)




```

-   Top BEL20 companies

```{r warning=FALSE, message=FALSE, echo=TRUE, collapse=TRUE}

top_companies_bel <- data_bel %>%  
  group_by(Nombre) %>% 
  summarise(average_price = mean(ultimo, na.rm = TRUE)) %>% 
  arrange(desc(average_price)) %>% 
  head(5)

colnames(top_companies_bel) <- c("Company", "Last Price") 
knitr::kable(top_companies_bel, caption = "Top 5 Companies in Belgium", align = "c")
```

#### **Top 5 companies for each European Stock Market**

```{r}


top_companies_ibex$Market <- "IBEX"
top_companies_bel$Market <- "BEL"
top_companies_cac$Market <- "CAC"
top_companies_ftse$Market <- "FTSE"
top_companies_atx$Market <- "ATX"


all_top_companies <- bind_rows(
  top_companies_ibex,
  top_companies_bel,
  top_companies_cac,
  top_companies_ftse,
  top_companies_atx
)

knitr::kable(all_top_companies, caption = "Top Companies in Each Stock Market", align = "c")

```
